Determination of the \ce{^{64}Zn},\ce{^{47}Ti}(n,p) Cross-Sections using a DD Neutron Generator for Medical Isotope Studies

### 2017-03-03 First_np_Paper/first_np_paper.tex
Updated fracplot and scatt_angle figures

@@

The D(D,n)\ce{^3He} reaction at 100 keV lab energy produces neutrons with energies ranging from 2.2 to 2.85 MeV, over an angular range of 0-180\degree\ in the lab frame-of-reference with respect to the incident deuteron beam. This distribution has been well documented \cite{Liskien_Paulsen_1973} and is shown in \autoref{fig:scatt_angle} for 100 keV incident deuteron energy.

\comment{These 2.2 to 2.85 MeV numbers do not quite correspond to the Figure. Addressing this with Joe.}

@@

Since the samples are separated by only  8 mm from the DD reaction surface they  subtend a fairly significant  (~28\degree) angular range and experience an impressive  (approximately $\sci{1.3}{7}$neutrons/cm$^2$ s) neutron flux. This stands in contrast to other measurements which feature collimated beams and significantly lower total neutron flux.

@@

\comment{Need to replace this figure w/ non-capitalized labels - this figure needs significant work, and I would appreciate anyone who can provide a better one}

@@

@@

While this shows that the sample foils experience a very narrow energy distribution of incident neutrons, an effective neutron energy window must be determined. The MCNP6 simulation shows an identical flux-weighted average neutron energy of 2.765 MeV for both the Indium and target foils to the 1 keV level. Due to the kinematics of DD neutron emission, $E_{max}$,  the maximum energy of a neutron subtending the target foils in this geometry is 2.783 MeV. For this maximum energy, the number of reactions induced in a foil (containing $N_i$ target nuclei) is given by:

@@

\comment{Regex to replace equations with LaTeX formats, add cross-references.} % [E,e]quation[^*}]    }

@@

\comment{Change \autoref{fig:frac_plot} text from the $\pm 1\sigma$ to 68.2\%}

>>>>

% Tweak sim for better inline text tilde
\newcommand{\mytilde}{\raisebox{0.5ex}{\texttildelow}}
% \newcommand{\mytilde}{\raise.17ex\hbox{$\scriptstyle‌​\sim$}}

@@

The D(D,n)\ce{^3He} reaction at 100 keV lab energy produces neutrons with energies ranging from 
% 2.2 to 2.85 MeV   (thin-target Liskien values)
% 2.18 to 2.78 MeV  (Liskien thick-target coefficient corrections to above)
2.18 to 2.78 MeV, over an angular range of 0-180\degree\ in the lab frame-of-reference with respect to the incident deuteron beam. This distribution has been well documented \cite{Liskien_Paulsen_1973} and is shown in \autoref{fig:scatt_angle} for 100 keV incident deuteron energy.

% \comment{These 2.2 to 2.85 MeV numbers do not quite correspond to the Figure. Addressing this with Joe.}

@@

Since the samples are separated by only  8 mm from the DD reaction surface they  subtend a fairly significant  (\mytilde 17\degree)
% the above figure assumes a 5mm diameter beam seperated by 8 mm from a 10 cm diameter target, looking at the angle between the two edges
angular range and experience an impressive  (approximately $\sci{1.3}{7}$neutrons/cm$^2$ s) neutron flux. This stands in contrast to other measurements which feature collimated beams and significantly lower total neutron flux.

@@

\comment{Need to replace this figure w/ non-capitalized labels - this figure needs significant improvement, and I would appreciate anyone who can provide a better one}

@@

\comment{\autoref{fig:mcnp_flux} to be updated with new data from Joe}

@@

While this shows that the sample foils experience a very narrow energy distribution of incident neutrons, an effective neutron energy window must be determined. The MCNP6 simulation shows an identical flux-weighted average neutron energy of 2.765 MeV for both the Indium and target foils to the 1 keV level. Due to the kinematics of DD neutron emission, $E_{max}$,  the maximum energy of a neutron subtending the target foils in this geometry is 2.783 MeV \cite{Liskien_Paulsen_1973}. For this maximum energy, the number of reactions induced in a foil (containing $N_i$ target nuclei) is given by:

@@

% \comment{Regex to replace equations with LaTeX formats, add cross-references.} % [E,e]quation[^*}]    }

@@

% \comment{Change \autoref{fig:frac_plot} text from the $\pm 1\sigma$ to 68.2\%, after using new A}
